%-------------------------
% Resume in LaTeX — Full / Complete Version (multi-page)
% Based on "Jake's Resume" template.
% Compile with: pdflatex resume-full.tex
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=1pt, topsep=4pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Chia-Yuan Chiang} \\ \vspace{1pt}
    \small +886 928 530 700 $|$ \href{mailto:johnjia9491@gmail.com}{johnjia9491@gmail.com} $|$
    \href{https://github.com/Jcsk7049}{github.com/Jcsk7049} $|$
    \href{https://linkedin.com/in/\%E5\%98\%89\%E5\%85\%83-\%E6\%B1\%9F-662764344}{LinkedIn} $|$
    Taipei, Taiwan
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Yuan Ze University}{Taoyuan, Taiwan}
      {B.S. in Electrical Engineering}{Sep. 2024 -- Sep. 2027 (Expected)}
    \resumeSubheading
      {Nangang Senior High School}{Taipei, Taiwan}
      {Electronics Technology}{Sep. 2020 -- Jun. 2023}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Undergraduate Researcher}{May 2025 -- Present}
      {Prof. Shu-Yen Lin's Lab, Yuan Ze University}{Taoyuan, Taiwan}
      \resumeItemListStart
        \resumeItem{Led an early-warning model for ICU Ventilator-Associated Pneumonia (VAP); designed a stay-level 5-fold cross-validation scheme to eliminate patient-level data leakage present in the public benchmark.}
        \resumeItem{Applied Integrated Gradients feature attribution to reduce the model to 4 non-invasive features; the resulting LSTM reached 0.98--0.99 AUROC at a 72-hour prediction horizon.}
        \resumeItem{Manuscript submitted to IEEE GCCE 2026.}
      \resumeItemListEnd

    \resumeSubheading
      {Engineering Advisor \& Systems Integrator}{2023 -- Present}
      {FRC Team 7645}{Taipei, Taiwan}
      \resumeItemListStart
        \resumeItem{Own robot system architecture: multi-sensor fusion, PID closed-loop motor control tuning, and software/hardware interface definitions.}
        \resumeItem{Introduced LLM-assisted tooling that cut iterative firmware debugging time by roughly one week; trained junior members to debug from root-cause analysis instead of trial-and-error.}
        \resumeItem{Rebuilt the team website, reducing repetitive PR/outreach inquiries.}
      \resumeItemListEnd

    \resumeSubheading
      {Competitor}{Jun. 2020 -- Sep. 2023}
      {Nangang Senior High School -- NK-MTC 7645}{Taipei, Taiwan}
      \resumeItemListStart
        \resumeItem{Generalist across LabVIEW/Arduino firmware, FRC electrical wiring, AutoCAD modeling, and 3D-printed mechanical parts.}
        \resumeItem{Competed in 2 FRC regional events (2020 CIT 5G Regional, 2022 Hon Hai Taiwan Regional) and represented the school at the National Skills Competition.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ICU VAP Early-Warning Model} $|$ \emph{TensorFlow/Keras, LSTM, Integrated Gradients}}{2025 -- Present}
          \resumeItemListStart
            \resumeItem{Single-center study (Far Eastern Memorial Hospital ICU, n=109); identified window-level cross-validation data leakage in the PREDICT benchmark (a patient's time windows split across train/test) and redesigned a stay-level 5-fold stratified CV that reflects true generalization to unseen patients.}
            \resumeItem{Used Integrated Gradients to drop a collinear redundant feature (mv\_total $\equiv$ Vt $\times$ RR) and reduced the model to 4 non-invasive features; final LSTM reached 0.99 AUROC at a 24-hour horizon, 0.98--0.99 across 6--72h.}
            \resumeItem{Outperformed LR/RF/SVM baselines at every prediction window under the same setup; manuscript submitted to IEEE GCCE 2026.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{PCB Defect Detection} $|$ \emph{Azure Custom Vision, Python}}{2025}
          \resumeItemListStart
            \resumeItem{Trained an object-detection model to localize PCB defects across 3 board types and 3 defect classes; first attempt on full-resolution images scored only 9.6\% mAP because each defect box (\textasciitilde60px) vanished after Custom Vision's resize.}
            \resumeItem{Fixed it with 600px defect-centered tiling, raising defect bounding-box area share from \textasciitilde2\% to \textasciitilde12\% of each tile; mAP went from 9.6\% to 81.9\%.}
            \resumeItem{Validated on held-out board types (06/07) unseen during training; reached 100\% precision, 69.7\% recall. Exported TensorFlow model.pb and ran inference in Colab with the official anchor/NMS decoder.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Open-Source QMK x STM32 Numpad} $|$ \emph{C, ChibiOS HAL, EasyEDA}}{2026}
          \resumeItemListStart
            \resumeItem{Adapted an open-source 17-key PCB in EasyEDA Pro for fabrication, hand-soldered the board, and flashed STM32F103 through the stm32duino bootloader.}
            \resumeItem{Reverse-engineered ChibiOS HAL config (chconf/halconf/mcuconf) to resolve build conflicts and timing issues between the open-source PCB and QMK firmware; reached stable USB HID enumeration.}
            \resumeItem{Got RGB Matrix working with a brightness cap to prevent LED over-current, plus live VIA/VIAL remapping without recompiling; fixed a top/bottom-layer footprint mirroring bug in the PCB design.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Swerve Drive Chassis (FRC)} $|$ \emph{LabVIEW, CNC, PID Control}}{2020 -- 2023}
          \resumeItemListStart
            \resumeItem{Designed and machined 3 generations of a swerve-drive chassis from scratch: kinematics, gear train, CNC/wire-EDM fabrication, and LabVIEW PID control.}
            \resumeItem{Gen-3 cut weight via 3D-printed gears, modularized drive/steer motor mounts (NEO or Falcon 500 interchangeable), and redesigned wheels for better grip; won Innovation in Control Award at 2022 FRC Taiwan Hon Hai Regional.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Job Radar} $|$ \emph{Python, Playwright, GitHub Actions, Cloudflare Pages}}{2026 -- Present}
          \resumeItemListStart
            \resumeItem{Built a personal job-listing aggregator scraping 104, Cake, and LinkedIn (\textasciitilde1,300 listings/day) via a daily GitHub Actions cron; reverse-engineered 104's internal SPA API after the legacy API was deprecated.}
            \resumeItem{Designed a config-driven scoring engine (role fit, location commute, experience threshold) and a static-site dashboard build pipeline with no backend or database.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{AWS x BitoPro Hackathon -- AI Fraud Detection}}{2026}
          \resumeItemListStart
            \resumeItem{Built an account risk-scoring dashboard (AUC 83.2\%) with 5-fold CV and decision-threshold tuning (optimal 0.24) over 12,753 user accounts.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.0in, label={}]
    \small{\item{
     \textbf{Languages \& Firmware}{: C/C++ (STM32/Cortex-M), Python, QMK/ChibiOS HAL, LabVIEW, Arduino/ESP32, UART} \\
     \textbf{Machine Learning}{: TensorFlow/Keras, LSTM/Time-Series, Feature Engineering, Signal Processing, Integrated Gradients/XAI, SHAP} \\
     \textbf{EDA / Hardware}{: Altium Designer, KiCAD, OrCAD, EasyEDA Pro} \\
     \textbf{Manufacturing}{: CNC Milling, Mastercam, 3D Printing, Laser Cutting, Welding, AutoCAD, Fusion 360, Autodesk Inventor} \\
    }}
 \end{itemize}

%-----------AWARDS & CERTIFICATIONS-----------
\section{Awards \& Certifications}
 \begin{itemize}[leftmargin=0.0in, label={}]
    \small{\item{
     2022 FRC Taiwan Hon Hai Regional -- Finalist Alliance \& Innovation in Control Award $\cdot$
     52nd National Skills Competition -- Team Project Category Representative (2022) $\cdot$
     2020 FRC CIT 5G Regional -- Excellence in Engineering (Industrial Design) Award
    }}
 \end{itemize}

\end{document}
